---
title: "NEON-capstone"
author: "Amy Hudson"
date: "June 23, 2016"
output: html_document
--- 

#NEON capstone 

just that plot or all of those bands
NDVI

NEON Phenology Observations are available for HARV, 2013 and 2014
LTER Pheno Data?
Pheno Cameras: harvardhemlock2 (Phenocam network) (write empty code to incorporate- they don't have photos for period of overlap)
NDVI? (2014)
LandSat? (2013 and 2014?)
MODIS?

https://public.etherpad-mozilla.org/p/HARV_phenology

Correlate each phenophase with NDVI 
Or create a vector

HARV: Prospect Hill Tract
42.541779  -72.173509
42.543716 -72.170825

Pheno observation vs phenocam
Pheno vs Elevation
Compare NEON Phenology with Harvard efforts... USNPN? 

Compare Observation data 

#Load Libraries
```{r load-libraries}
library(raster)
library(rhdf5)
library(rgdal)
library(neonAOP)
library(rgeos)

```

#Read in NEON Phenology Observations 
```{r input-pheno-obs}
pheno.spatial <- read.csv("../NEONdata/HARV Phenology/NEON.D01.HARV.DP1.10055.001.phe_perindividual.csv") #upload individualID, decimalLatitude, decimalLongitude, elevation

pheno.phase <- read.csv("../NEONdata/HARV Phenology/NEON.D01.HARV.DP1.10055.001.phe_statusintensity.csv") #upload individualID, dayOfYear, phenophaseName, phenophaseStatus 

myvars <- c("individualID","dayOfYear","phenophaseName","phenophaseStatus")
pheno.phase.sub <- pheno.phase[myvars]
names(pheno.phase.sub) <- c("individualID","dayOfYear","phenophaseName","phenophaseStatus")

myvars <- c("individualID", "decimalLatitude", "decimalLongitude", "elevation")
pheno.spatial.sub <- pheno.spatial[myvars]
names(pheno.spatial.sub) <- c("individualID", "decimalLatitude", "decimalLongitude", "elevation")

#Clean up phenophases to only those recorded as yes's
pheno.phase.sub$phenophaseStatus[pheno.phase.sub$phenophaseStatus == 'no'] <- NA
pheno.phase.sub$phenophaseStatus[pheno.phase.sub$phenophaseStatus == 'uncertain'] <- NA
pheno.phase.sub$phenophaseStatus[pheno.phase.sub$phenophaseStatus == 'missed'] <- NA

names(pheno.phase.sub) <- c("individualID","dayOfYear","phenophaseName", "phenophaseStatus")
#complete phenophase observations
pheno.phase.comp <- pheno.phase.sub[complete.cases(pheno.phase.sub),]
pheno.phase.comp$phenophaseStatus <-  NULL
  
pheno <- merge(pheno.phase.comp, pheno.spatial.sub, by = "individualID")
View(pheno)


```


```{r hist}



```


```{r scrap}

pheno.phase.length <- 6154 #length(pheno.phase.comp) 
pheno.spatial.length <- 204 #length(pheno.spatial.sub)
lat<- rep(NA,pheno.phase.length)
lon <- rep(NA,pheno.phase.length)
ele <- rep(NA,pheno.phase.length)
              

for(i in 1:pheno.phase.length){
  for(j in 1:pheno.spatial.length){
    if(pheno.phase.sub$individualID[i] == pheno.spatial.sub$individualID[j]){
    lat[i] <- pheno.spatial.sub$decimalLatitude[j] 
    lon[i] <- pheno.spatial.sub$decimalLongitude[j]
    ele[i] <- pheno.spatial.sub$elevation[j]
    } else{
    }
  }
}
pheno <- cbind(lat,lon,ele)


#summary graphs
#identifying phenophases
summary(pheno.phase$phenophaseName)


######
#Attach Lat Lon with phenophase data

by phenophaseName mean dayOfYear for uid 
(attach lat lon to pheno.phase.sub uid)

falling_leaves <- pheno.phase.comp %>%
group_by(phenophaseName) %>%
  summarise(mean(dayOfYear))


insitu_meanE_meanN_maxStemHeight <- veg1 %>%
  group_by(plotid) %>%
  summarise(mean(easting),mean(northing),max(stemheight))

names(insitu_meanE_meanN_maxStemHeight) <- c("plotid","easting","northing","insitu_maxHt")

```





#subset for elevation data (raster)

#insert and save as a raster
each phenophase can be a raster 


##NDVI for SJER but code for when available at harvard
```{r NDVI}

#read in NDVI raster
ndvi <- raster("../NEONdata/D17-California/SJER/2013/spectrometer/veg_index/SJER_NDVI.tif")

#imagine multiple NDVI files


#cut off ndvi at different growing thresholds

```

##Modify Holly's Landsat Thermal and CHM for HARV pheno spatial scale
```{r landsat-plus-chm-mod-spatial}

thermal <- raster("../NEONdata/HARV_thermal.TIF")
raster("")

```

#Phenopix package



